Boutiques: a flexible framework for automated application integration in computing platforms

### 2016-11-01 paper.tex
Added intro to section 2

Define ``the platform'', i.e. the entity that will run applications.
\begin{itemize}
\item JSON manifest
\item Link to container
\item Invocation schema
\end{itemize}

@@

\section{Implementation and Evaluation}

@@

@@

\subsection{Platforms}

>>>>

The application is described with a \emph{manifest} that specifies the
command-line template, inputs and outputs. The manifest may point to a
container where the application and all its dependencies are
installed. It may also contain an invocation schema used for input
validation. At runtime, the execution \emph{platform} builds the
application command line from the manifest and values entered by the
user. The platform runs the command line on the execution
infrastructure, e.g., a server, a cluster or a cloud, within a
container whenever available. To build and run the command line, the
platform may rely on the Boutiques \emph{core tools}, in particular on
the Boutiques validator and local executor. Application manifests may
be stored in the \emph{repository}, which provides additional features.

@@

@@

\section{Results}

@@

\subsection{Supported platforms}
